### 2020-05-31 paper.tex
Its about RxJS-base Applicaitons in general

	\Large{Workshop Paper}
	\par
	\Huge{Debugging of RxJS-based Frontend Web Applications}
	\par
	\vspace{2ex}

@@

This lack of specific knowledge about RP concepts in traditional debugging utilities does often end in time-consuming debugging sessions, as we can confirm from our own experience. Previous research has looked into this field \cite{10.1145/2577080.2577083} \cite{10.1145/2884781.2884815} \cite{10.1145/3180155.3180156} over the past years already. We will revisit their results in this paper and elaborate on the particular challenges of debugging RAs using RxJS for frontend web applications.

@@

\begin{itemize}
	\item \emph{RQ1: What challenges do frontend engineers face when debugging RxJS-based code?}
\end{itemize}

@@

\begin{itemize}
	\item \emph{RQ2: How can the experience of frontend engineers during debugging of RxJS-based code be improved?}
\end{itemize}

@@

\begin{itemize}
	\item \emph{RQ3: What is the impact of a proposed solution on the debugging experience of a frontend engineer?}
\end{itemize}

@@

We have talked to multiple people in order to understand how software engineers, and in particular frontend engineers, apply RP using RxJS for building applications. We have looked into how they debug their applications and could identify several struggles they have to overcome in this process. We could prove that the engineers inevitably tend to modify their source code once they do not understand how the RP runtime propagates values through its internal data-flow graph by observing professionals in an observational study.

>>>>

	\Large{Workshop Paper}
	\par
	\Huge{Debugging of RxJS-based Applications}
	\par
	\vspace{2ex}

@@

This lack of specific knowledge about RP concepts in traditional debugging utilities does often end in time-consuming debugging sessions, as we can confirm from our own experience. Previous research has looked into this field \cite{10.1145/2577080.2577083} \cite{10.1145/2884781.2884815} \cite{10.1145/3180155.3180156} over the past years already. We will revisit their results in this paper and elaborate on the particular challenges of debugging RAs implemented using RxJS.

@@

\begin{itemize}
	\item \emph{RQ1: What challenges do software engineers face when debugging RxJS-based code?}
\end{itemize}

@@

\begin{itemize}
	\item \emph{RQ2: How can the experience of software engineers during debugging of RxJS-based code be improved?}
\end{itemize}

@@

\begin{itemize}
	\item \emph{RQ3: What is the impact of a proposed solution on the debugging experience of a software engineer?}
\end{itemize}

@@

We have talked to multiple people in order to understand how software engineers apply RP using RxJS for building applications. We have looked into how they debug their applications and could identify several struggles they have to overcome in this process. We could prove that the engineers inevitably tend to modify their source code once they do not understand how the RP runtime propagates values through its internal data-flow graph by observing professionals in an observational study.
